Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-21 cav2017/cav2017.tex
Final reduction on 3.5

\item {\bf Overflow:}
  %Another source of error introduced by Finite Word Length representations is that of overflow.
  The finite word length set a
maximum representable number in the domain ($\pm 2^{I-1}+1-2^{-F}$), which means that any number outside this range
cannot be represented by the domain (\emph{eg} $\delta=x-2^{I-1}+1-2^{-F}$). Our tool currently assumes no saturation
function and verifies that no state overflows.
\end{enumerate}

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Fixed word length effects on matrix multiplications}
\label{sec:cof_fwl}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
Thus far we have presented a verification procedure for a digitalized plant in a continuous space (\emph{ie} the
range of the quatizers is still $\mathbb{R}$. The next step we must reaize is that the controller 
exists in a digital program, hence its domain is $\mathbb{R}\langle I,F\rangle$. We have $\mat{A},\mat{B},\vec{x} \in \mathbb{R}^*$, $\mat{K}_d,\vec{u} \in \mathbb{R}\langle I,F\rangle^*$
Where $*$ represents the appropriate dimension for each matrix/vector.
Unfortunately this means that although combined matrices such as $\mat{A}_t$ are in the reals, they suffer from
the fixed word restrictions in their composing matrices.
The second effect corresponds to the rounding errors in the calculation of $\hat{x}_{k+1}, u_k$. These will introduce a new source of quantiztion noise which we may denote $\vec{\nu}_3 \in [-q_3\ \ q_3]$.
The estimation of $\hat{\vec{x}}$ corresponds to the sum of three matrix-vector multiplications. Each of these has a coefficient-wise error bound $c_{min}$. Hence the overall $\overline{\delta}_{\hat{x}}=3nc_{min}$. The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=nc_{min}+\sum_{k=1}^nc_k\overline{\delta}_{\hat{x}}=(3|\mat{K}|_1+1)n2^{-F}$

>>>>

\item {\bf Overflow:}
  %Another source of error introduced by Finite Word Length representations is that of overflow.
  The finite word length set a
maximum representable number in the domain ($\pm (2^{I-1}+1-2^{-F})$), which means that any number outside this range
cannot be represented by the domain. Our tool currently assumes no saturation
function and verifies that no state overflows.
\end{enumerate}

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Fixed word length effects on matrix multiplications}
\label{sec:cof_fwl}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
Thus far we have presented a verification procedure for a digitalized plant in a continuous space (\emph{ie} the
range of the quatizers is still $\mathbb{R}$. The next step we must reaize is that the controller 
exists in a digital program, hence its domain is $\mathbb{R}\langle I,F\rangle$. We have $\mat{A},\mat{B},\vec{x} \in \mathbb{R}^*$, $\mat{K}_d,\vec{u},\hat{\vec{x}}=\mathcal{F}\langle I,F \rangle(\vec{x}) \in \mathbb{R}\langle I,F\rangle^*$
Where $*$ represents the appropriate dimension for each matrix/vector.
Unfortunately this means that although the closed loop dynamics are in the reals, they suffer from
the fixed word restrictions in their composing elements.
Apart from the quantization errors $q_1,q_2$ there are rounding errors in the calculation of $u_k$. These will introduce a new source of quantization noise which we may denote $\vec{\nu}_3 \in [-q_3\ \ q_3]$.
The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=(|\mat{K}|_1+1)c_m$
